\pkg{partykit}: A Modular Toolkit for Recursive Partytioning in \proglang{R}

### 2014-10-22 pkg/partykit/inst/mloss/letter_mloss2.tex
forgot
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@625 255f4249-2263-4417-b1ea-8498779e27a7

The package web page is \texttt{http://CRAN.R-project.org/package=partykit}
and points to the revised version 0.8-1 distributed under the GPL (2 or 3).
This version is also uploaded for review.

>>>>

The package web page is \texttt{http://CRAN.R-project.org/package=partykit}
and points to the revised version 0.8-2 distributed under the GPL (2 or 3).
This version is also uploaded for review.
